The Gillespie Algorithm: Stochastic Modeling of Molecular Reaction Networks

### 2024-11-26 test.Rmd
added rough observations to test.rmd

```{r graph_1, echo=FALSE, warning=FALSE, message=FALSE}
# Reshape data for plotting
simulation_long <- melt(simulation, id.vars = "Time")
# Plot results
ggplot(simulation_long, aes(x = Time, y = value, color = variable)) +
  geom_line() +
  labs(
    title = "Dimerization Reaction Set Simulation",
    x = "Time",
    y = "Molecule Count",
    color = "Species"
  ) +
  theme_minimal()
```
```{r}
# Display the first few rows of the simulation data
knitr::kable(head(simulation), format = "html", caption = "Simulation Results (First Few Rows)")
```

>>>>

```{r graph_1, echo=FALSE, warning=FALSE, message=FALSE}
# Reshape data for plotting
simulation_long <- melt(simulation, id.vars = "Time")
# Plot results
ggplot(simulation_long, aes(x = Time, y = value, color = variable)) +
  geom_line() +
  labs(
    title = "Dimerization Reaction Set Simulation",
    x = "Time",
    y = "Molecule Count",
    color = "Species"
  ) +
  theme_minimal()
```
```{r}
# Display the first few rows of the simulation data
knitr::kable(head(simulation), format = "html", caption = "Simulation Results (First Few Rows)")
```
###Observations
1.**Logarithmic Growth**
Both CPD and 64-PP formation follow logarithmic growth, as expected under specific UV radiation according to previously reported quantum yields (Martinez-Fernandez and Improta, 2022; Mouret et al., 2006). The number of reactions per unit time plateaus as the pyrimidine pairs decrease, consistent with the propensity functions.

2. **Stochastic Fluctuations**
Due to the stochastic nature of molecular reactions, this algorithm reflects fluctuations of photodimerization as it models the probabilistic process of each reaction.

3. **Time Steps and Reaction Events**

###Biological Significance
-**Photodimerization**
As pyrimidine photodimerization transforms two pyrimidine monomers into a dimer, this simulation has accurately represented the formation of two possible dimers, CPD and 64-PP, from pairs of thymine monomers. 
-**Real-World Application**
Dimerization is widely studied, as it can lead to DNA mutations causing skin cancer. 
This algorithm can be further adjusted to show molecular reactions with various molecular species and reaction channels.
